MS_Intro_Short

### 2022-05-16 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
refocus on he

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019]. Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equiped for this challenge[@RN22;@RN23]. The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems. To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].

Realising significant improvements in population mental health may in part depend on gaining better understanding of the systems in which mental disorder emerges and is treated [@Fried2020]. Currently, the theoretical basis for understanding these systems is weak [@RN2111]. Strikingly, it remains unclear why increased investments in mental health care have yet to discernably reduce the prevalence and burden of mental disorders[@RN26].  The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42]. There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].

Mental health simulation studies rarely explore the features and behaviours of complex systems [@RN73], with mental health economic models predominantly addressesing issues relating to the affordability and value for money of individual programs [@RN34]. Single purpose models that assume static systems, even when sufficiently robust to be formally incorported into Government resource planning processes, may be inadequate for the decision support needs of policymakers and service planners seeking to successfully identify, prioritise, sequence and target multiple elements of complex reform programs [@PC2020].

Multi-application, dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policy settings that static models of isolated scenarios cannot [@Occhipinti2021]. However, greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. The complexity of multi-application systems models may make them particularly prone to errors [@Saltelli2019], thus requiring greater investments in model transparency and validation [@Eddy2012]. These types of models can be highly resource intensive to develop and may also never be truly "finished", instead requiring ongoing updates to remain relevant to evolving decision contexts [@Jenkins2021] and to meet additional feature requests from end-users. The development, validation and maintenance of these types of models may be simply too onerous and long term a burden to remain the responsibility of a single modelling team and might benefit from collaborations across multiple modelling teams, and perhaps the general mental health modelling field. Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure multi-purpose models can address priority decision topics and have user-interfaces that meet the needs of non-technical users.

Open source frameworks, which have been recommended for the development of mental health modelling field [@RN73], have the potential to help address a number of these challenges. Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features. They may also have educational value in developing the health systems modelling field [@Dunlop2017]. However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.

>>>>

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models have become an essential tool for healthcare policy development [@Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are often poorly reproducible [@Jalali2021; @McManus2019] and may be infrequently updated or revised [@Sampson2017]. To address these issues, there is increasing in principle support for open source health economics models (OSHEMs) that grant open access to and liberal permission to re-use model source code [@Pouwels2022]. However, in-practice implementation of OSHEMs remains rare [@Emerson2019]. Some resistence to adoption centers on.... [@Padula2017] .

A major shift in how health economic models are implemented.....They may also have educational value in developing the health systems modelling field [@Dunlop2017]. However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.

The health economics field i

copyrights, model misuse, confidential data, software, and time/resources [@Wu2019]
cooperation [@Arnold2010]
coding framework / guidance [@Alarid2019]
10 rules [@Erdemir2020]
Sys review
Over the last decade there have been
the potential to increase the transparency, reproducibility and reuse of health economic analyses.

Open source frameworks, which have been recommended for the development of mental health modelling field [@RN73], have the potential to help address a number of these challenges. Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.
